---
title: "Data Products 3"
author: "Justin Desrosier"
date: "08/06/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera - Developing Data Products Week 4, Assignment 3

Reproducible Pitch

## Reference Course Material

This Shiny application was built using methods learned from the Regression Models Course.

The application uses the dataset, mtcars, built-in to R.

The presentation was developed using Bookdown's ioslides and published using Rpubs.

## mtcars Dataset

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles.

```{r cars, echo = TRUE}
library(datasets)
head(mtcars, 3)
```

## mtcars Dataset - Format

**A dataframe with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2] | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

## Shiny Application Main Code

        ```r
formulaTextPoint <- reactive({
        paste("mpg ~", "as.integer(", input$variable, ")")  })

fit <- reactive({
        lm(as.formula(formulaTextPoint()), data=mpgData)  })
...
output$fit <- renderPrint({
        summary(fit()) })

output$mpgPlot <- renderPlot({
        with(mpgData, {
                plot(as.formula(formulaTextPoint()))
                abline(fit(), col=2)
        })  })
```
